---
title: "first-analysis"
author: "surbut"
date: "2018-09-28"
output: workflowr::wflow_html
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)

```

## R Markdown

Here I load the data from my Data directory within this project. Note the full path. I don't know why it doesn't work from relative. 

In this experiment, the tail vein of a mouse is transfected with an ovarian tumor cell-pellet "seed", and all the cells are labeled 'clones.'


```{r Dataentry}
#install.packages("workflowr")
#library("workflowr")
#temp = list.files(path="~/Dropbox/Pearson_Data/Data/",pattern="Decon*",full.names = TRUE)

mat=read.csv("~/myproject/data/M3_Mouse.csv",header = T)[,-1];
rownames(mat)=mat[,1];mat=mat[,-1]
```

We can see that the barcodes are in the rows and the tissues are in the columns, and that the dimensions are as follow. WE are limited to K=5.

```{r,echo=FALSE}
#<!Combine into merged data set, you can see the data is actually in a different order than 1:10;>
#temp
head(mat)
```
 
```{r, eval=F,echo=F}
#Here we combine the dfs into a list and merge shared rows.
myfiles = lapply(temp, function(x){
  a=read.csv(file=x,header = T);
  return(a[,c(2:3)])})



b=Reduce(function(x,y) merge(x, y, by = "full_label", all.x = TRUE, all.y = TRUE),myfiles) 



b[is.na(b)] <- 0
rownames(b)=b[,1];b=b[,-1]

mat=as.matrix(b)
#You can see that the barcodes are in the rows and the tissue samples are in the columns, in the order posted above, 
head(mat)


#and that the rows correspond to unique barcodes:

length(rownames(b))

length(unique(rownames(b)))

```

There are `r dim(mat)[2]` unqiue barcodes. Noww we install some packages necessary for the GOM model according to **CountClust** vignette.

```{r eval=T,echo=FALSE}


# install.packages("maptpx")
#source("https://bioconductor.org/biocLite.R")
#biocLite("CountClust")
library('CountClust')


library("RColorBrewer")
```

To fit for multiple K, we apply the following model and consider how the different clones fall into patterns characterized by tissue-sepcific expression. We cna see that each cluone can have membership in up to 10 clusters, where each cluster is characterized by predilection to a particular tissue or group of tissues. WE can then consider which clusters are most popular, and examine the tissue patterns they demonstrate.

```{r,eval=T}
#fits <- lapply(2:10, function(k) FitGoM(mat,K=k, tol=1))## try over different Ks
fit=FitGoM(mat,K=5, tol=1)$fit

omega <- fit$omega


# annotation <- data.frame(
#  sample_id = rownames(omega),
#  tissue_label = factor(rownames(omega),
#                        levels = rownames(omega)))
# 
# rownames(omega) <- annotation$sample_id;
# 
# 
# sample_id <- rownames(omega)

#annotation$sample_id <- as.character(annotation$sample_id)

StructureGGplot(omega = omega,
                #annotation = annotation,
                palette = c(brewer.pal(8, "Accent")),
                yaxis_label = "Clone Number",
                order_sample = TRUE,
                #sample_order_opts=4,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"),figure_title = "Clonal Membership in Clusters")
```

We can examine the `omega` matrix to try and understand the proportional membership of every clone, and overall enrichemnt of each cluster.

```{r, eval=T,echo=T}
head(omega[1:10,])
```

For example, clone with barcode `1_9115` has 44% membership in cluster 1, 52.8% membership in cluster 3, and trivial membership in other clusters. To look at overall proportions of membership in each cluster, we can consider the overall proportion of clones (weighted by their cluster memebrship) in eahc cluster. WE see that Cluster 1 is the most popular followed by cluster 2, etc.

```{r}
pie(colSums(omega/nrow(mat)),main="Cluster Membership",col=brewer.pal(8, "Accent"))
```



We extract the top clones driving each cluster using the ExtractTopFeatures functionality of the CountClust package. We first perform the cluster annotations from the GoM model fit with `k=5` on the clone data. We can see that some of the clusters have strong  lung expression, and some have more tissue specific expression in adrenal, left ovary, liver or right ovary. 


```{r, eval=T,echo=FALSE}
#install.packages("gplots")
library(gplots)
library('dplyr')
library(lattice)
theta_mat <- fit$theta;
rownames(theta_mat)=colnames(mat)
n=nrow(theta_mat)
col=colorRampPalette(c('dark red','white','dark blue'))
lat=theta_mat
print(levelplot(lat[n:1,],col.regions=col,#col.regions = clrs,
                xlab = "",ylab = "K",colorkey = TRUE))
#axis(1,at = 1:5,labels = rownames(theta_mat))
# 
# heatmap.2()
# 
# col=colorRampPalette(c('dark red','white','dark blue'))
# 
# (theta_mat,colorRampPalette(c('dark red','white','dark blue')))
# 
# top_features <- ExtractTopFeatures(theta_mat, top_features=100,
#                                    method="poisson", options="min");
# 
# clone_names=rownames(b)
# cell_list <- do.call(rbind, lapply(1:dim(top_features$indices)[1],
#                         function(x) clone_names[top_features$indices[x,]]))
# 
# tmp <- do.call(rbind, lapply(1:5, function(i) toString(cell_list[,i])))
# rownames(tmp) <- paste("Cluster", c(1:5))
# #library(knitr)
# #install.packages("kableExtra")
# 
# library("kableExtra")
# rownames(tmp) <- paste("Cluster", c(1:5))
# tmp %>%
#   kable("html") %>%
#   kable_styling()
```

```{r,eval=F,echo=F}
# svd.obj=svd(x = mat)
# 
# labs= c("cell_pellet", "lung_5","liver_5","rt.ovary_5","sc_tumor_2","omentum_5","sc_tumor", "lung_m3","liver_m3","right_ovary_3", "left_ovary_3", "adrenal_3", "lung_4","rt_ovary_4")
# 
# v=svd.obj$v;u=svd.obj$u;d=svd.obj$d
# plot(v[,2],v[,3])#,ylim=c(-0.5,1),xlim=c(-1,0.5))
# text(v[,2],v[,3],labs, cex=0.6, pos=4, col="red")
# 
# 
```
