---
title: "first-analysis"
author: "surbut"
date: "2018-09-28"
output: workflowr::wflow_html
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)

```

## R Markdown

Here I load the data from my Data directory within this project:

```{r Dataentry}
#install.packages("workflowr")
#library("workflowr")
temp = list.files(path="~/Dropbox/Pearson_Data/Data/",pattern="Decon*",full.names = TRUE)
```
Combine into merged data set, you can see the data is actually in a different order than 1:10;
```{r}
temp
```
Here we combine the dfs into a list and merge shared rows. 
```{r,warning=F}
myfiles = lapply(temp, function(x){
  a=read.csv(file=x,header = T);
  return(a[,c(2:3)])})



b=Reduce(function(x,y) merge(x, y, by = "full_label", all.x = TRUE, all.y = TRUE),myfiles) 



b[is.na(b)] <- 0
rownames(b)=b[,1];b=b[,-1]

mat=as.matrix(b)
```

You can see that the barcodes are in the rows and the tissue samples are in the columns, in the order posted above, 
```{r }
head(mat)
```

and that the rows correspond to unique barcodes:
```{r}
length(rownames(b))

length(unique(rownames(b)))

```

There are `r dim(b)[2]` unqiue barcodes. NOw we install some packages necessary for the GOM model according to **CountClust** vignette.

```{r eval=T}


# install.packages("maptpx")
#source("https://bioconductor.org/biocLite.R")
#biocLite("CountClust")
library('CountClust')


library("RColorBrewer")
```

To fit for multiple K:

```{r,eval=T}
fits <- lapply(8:10, function(k) FitGoM(t(b),K=k, tol=1))## try over different Ks
#fit=FitGoM(t(b),K=4, tol=1)

omega <- fits[[3]]$fit$omega
fitGOM=fits[[3]]$fit
attributes(fitGOM)

annotation <- data.frame(
 sample_id = rownames(omega),
 tissue_label = factor(rownames(omega),
                       levels = rownames(omega),
labels=rev( c("cell_pellet", "lung_5","liver_5","rt.ovary_5","sc_tumor_2","omentum_5","sc_tumor", "lung_m3","liver_m3","right_ovary_3", "left_ovary_3", "adrenal_3", "lung_4","rt_ovary_4"))))

rownames(omega) <- annotation$sample_id;


sample_id <- rownames(omega)

annotation$sample_id <- as.character(annotation$sample_id)

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = c(brewer.pal(8, "Accent"),brewer.pal(8, "Accent")),
                yaxis_label = "Development Phase",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))
```

Let's plot a heatmap of the clones driving the clusters:

```{r}

library('lattice')
barplot(height = fitGOM$theta,col = brewer.pal(9,"Greens"),main="CloneRepresentation per Cluster")


```

We extract the top clones driving each cluster using the ExtractTopFeatures functionality of the CountClust package. We first perform the cluster annotations from the GoM model fit with $k=10` on the clone data: 


```{r, eval=T}
#install.packages("dplyr")
library('dplyr')

theta_mat <- fitGOM$theta;
top_features <- ExtractTopFeatures(theta_mat, top_features=100,
                                   method="poisson", options="min");

clone_names=rownames(b)
cell_list <- do.call(rbind, lapply(1:dim(top_features$indices)[1],
                        function(x) clone_names[top_features$indices[x,]]))

tmp <- do.call(rbind, lapply(1:5, function(i) toString(cell_list[,i])))
rownames(tmp) <- paste("Cluster", c(1:5))
#library(knitr)
#install.packages("kableExtra")

library("kableExtra")
rownames(tmp) <- paste("Cluster", c(1:5))
tmp %>%
  kable("html") %>%
  kable_styling()
```
Let's look at the PC of the matrix:

```{r,eval=T}
svd.obj=svd(x = mat)

labs= c("cell_pellet", "lung_5","liver_5","rt.ovary_5","sc_tumor_2","omentum_5","sc_tumor", "lung_m3","liver_m3","right_ovary_3", "left_ovary_3", "adrenal_3", "lung_4","rt_ovary_4")

v=svd.obj$v;u=svd.obj$u;d=svd.obj$d
plot(v[,2],v[,3])#,ylim=c(-0.5,1),xlim=c(-1,0.5))
text(v[,2],v[,3],labs, cex=0.6, pos=4, col="red")


```
